The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-01-19 Ben_Manuscripts/transport/Outline.tex
new demos and minor fixes
Upates to methods and addition of results

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work (reference to structure
	paper).
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond, with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

  \subsubsection*{Modeling the Continuous Time Random Walk}\label{method:CTRW}

  A continuous time random walk (CTRW) is a stochastic anomalous diffusion
  process characterized by a distribution of hop lengths and dwell times.
  \begin{itemize}
	\item The MSD for an anomalous diffusion process is of the form $$t^\alpha$$
	\item A value of $\alpha < 1$ tells us that the molecules exhibits subdiffusion
	\item Subdiffusive, non-ergodic processes with uncorrelated steps help distinguish 
	a CTRW from other anomalous subdiffusive process such as fraction brownian motion 
	and random walks on a fractal.
	\item See supporting info for proof of the system's non-ergodicty and uncorrelated steps.
  \end{itemize}

  We fit our data to a CTRW model by using our data in order to construct 
  dwell time and hop length distributions.
  \begin{itemize}
	\item We use the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories. (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item We have limited data, so we attempted to approximate these distributions
	with known continuous probability densities.
	\item Incorporates effects of `aging' since it samples long dwell times
	\item For solutes in our system the distribution of hop lengths is
	well-represented by a Gaussian distribution 
	\item The distribution of dwell	times is expected to fit a heavy tailed distribution: 
  \end{itemize}

  \begin{equation}
	Ax^{(-1 - \alpha)}
  \end{equation}

  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
  magnitude longer than our molecular simulations. 
  \begin{itemize}
	\item We constructed trajectories by generating sequences of dwell times 
        and hop lengths randomly sampled from our fit distributions.
	\item For time scales much greater than the characteristic time of our
	dwell time distribution, solutes exhibit Brownian motion. 
	\item The MSD curve becomes linear
	\item We fit a line to the MSD curve and used the Einstein relationship
	to relate its slope to the macroscopic diffusion coefficient.
	\item We found convergence of the value of the diffusion coefficient 
	calculated in this way afer x steps (See Supporting Information)
  \end{itemize}

@@

  We quantified the coordination of solutes with surrounding molecules and
  functional groups in two ways.
  \begin{itemize}
	\item By counting the number of coordinated molecules to a given solute
	based on a distance cut-off. Gives frame-by-frame information. 
	\item By averaging 3D spherical radial distribution function calculated for
	each solute.
  \end{itemize}

@@

  \subsection{Macroscopic Diffusion Coefficients}

  \subsubsection{Simulated Predictions}\label{section:D_macro}

@@

  \clearpage
  \bibliography{llc}

>>>>

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimzation.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using long simulations, on the order of
	1 microsecond
	\item .mdp files are in the supporting information % with pressure controlled by the Parrinello-Rahman barostat.
  \end{itemize}

  \subsubsection*{Modeling subdiffusion}\label{method:CTRW}

  Solutes in our H\textsubscript{II} LLC membrane exhibit subdiffusive
  behavior, a type of anomalous diffusion. 
  \begin{itemize}
  	\item During an anomalous diffusion process, the mean squared displacement (MSD)
  	does not grow linearly with time, rather it is of the form:
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 0$ is characteristic of Brownian and superdiffusive
	motion respectively.
  \end{itemize}

  \noindent We calculated both the ensemble-averaged and time-averaged MSDs
  of the simulated trajectories.
  \begin{itemize}
	\item The ensemble-averaged MSD measures the displacement of a particle from its initial
	position~\cite{meroz_toolbox_2015} and can be written as
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
%	\item The average MSD calculated in this way recovers the form of
%	Equation~\ref{eqn:msd_form}. % time-averaged should recover it too for FBM 
	\item The time-averaged MSD measures the displacement between all possible time lags
	and can be written as
	\begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
%	\item The time-averaged MSD becomes linear in our simulations,
%	therefore we can fit a line to its slope in order to estimate the macroscopic
%	diffusivity of the particle.
	%BJC: this needs more justification. Not many people have done it
	%BJC: could also not report them as diffusivities. Comparison of total MSD
	% should give same information
	% Linear region probably exists because dwell times on the order of large lag times
	% become negligible
  \end{itemize}

  \noindent Three common mathematical models for modeling anomalous subdiffusion processes include 
  continuous time random walks (CTRW), fractional Brownian motion (FBM) and
  random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  \begin{itemize}
    \item FBM is common in crowded, viscoelastic environments where each step comes 
    from a Gaussian distribution but is anti-correlated to its previous 
    step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
    \item A CTRW is characterized by a distribution of hop lengths and 
    dwell times, where each each step is characterized by independent random draws from 
    each distribution.\cite{montroll_random_1965,morrin_three_2018}
    \item An RWF is imposed by a system's geometry. Systems with tortuous pathways and dead
    ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
    \item The processes described above can happen alone or in combination.  	
  \end{itemize}

  \noindent We believe that solutes in the system studied here exhibit subordinated 
  fractional Brownian motion (sFBM) where the parent process is FBM and the 
  leading process is a CTRW. 
  \begin{itemize}
  	\item The ensemble-averaged MSD differs from the time-averaged MSD, which
  	is indicative of non-ergodicity, a trait inherent to CTRWs but not FBM or RWFs.~\cite{thiel_weak_2014}
  	\item We also observe non-stationary $z$-coordinate traces of each solute's
  	center of mass (COM). %BJC: figure of a z-coordinate trace in main text or in supporting info
  	\item For a pure CTRW, the time-averaged MSD should be linear.
  	~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  	\item However, a typical time-averaged solute MSD is sublinear (see supporting
  	information), which suggests that there is another underlying subdiffusive mechanism.
  	\item The hop lengths recorded after each dwell period are anti-correlated (See supporting information)
  	\item Given the viscoelastic nature of the monomers in our system, we believe
  	the hop lengths can be modeled with FBM. 
 	\item For subordinated FBM, it can be shown that
  	\begin{equation}
  	\langle x^2(t) \rangle \simeq t^{\alpha\beta}
  	\end{equation}
  	where $\alpha$ is the anomalous exponent characteristic of the leading CTRW process
  	and $\beta$ is the anomalous exponent characteristic of the parent FBM process. 
  \end{itemize}

  \noindent We can characterize a CTRW process using the parameters which describe its
  dwell time and hop length distribution.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints in solute trajectories.\cite{truong_ruptures:_2018} (See Supporting Information for more
	details on chosen parameters. i.e. type of cost function, cost function penalty
	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
	\item For solutes in our system, the distribution of hop lengths is
	well-represented by a Gaussian distribution.~\cite{metzler_random_2000,
	metzler_anomalous_2014,neusius_subdiffusion_2009}
	\item We are most interested in the standard deviation, $\sigma$, of the 
	hop length distribution.
	\item The distribution of dwell	times is expected to fit a power law (or heavy-tailed)
	distribution proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
	\item Because we are limited to taking measurements at discrete values
	dictated by the output frequency of our simulation trajectories, we fit the
	empirical dwell times to a discrete power law distribution whose maximum
	likelihood $\alpha$ parameter we calculated by maximizing the following
	likelihood function: 
        \begin{equation}
	\mathcal{L}(\beta) = -n\text{ln}\zeta(\beta, x_{min}) -
	\beta\sum_{i=1}^{n} \text{ln}~x_i 
	\label{eqn:powerlaw_likelihood}
	\end{equation}
	where $\beta = 1 + \alpha$, $x_i$ are collected dwell time data points,
	$n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
	where $x_{min}$ is the smallest measured value of
	$x_i$.~\cite{clauset_power-law_2009} 
	\item We obtained distributions of the hop length standard deviations, $\sigma$, and
	$\alpha$ using statistical bootstrapping.\cite{efron_introduction_1994} 
  \end{itemize}

  \noindent FBM processes can be described using the Hurst parameter, $H$, where 
  $H = \beta/2$.
  \begin{itemize}
  	\item Brownian motion is recovered for $H = 0.5$
	\item The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
    \begin{equation}
	\gamma(k) = \dfrac{1}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
	\label{eqn:autocovariance}
	\end{equation}
	where $k$ is the number of increments between hops.
	\item We obtained H by performing a least squares fit of Equation~\ref{eqn:autocovariance}
	to the empirically measured autocovariance function.
	\item We used statistical bootstrapping to generate a distribution of $H$ 
	values. %BJC: can provide more detail in supporting or just reference python script
  \end{itemize}

%  We generated distributions of parameters for the dwell time and hop length
%  distributions using statistical bootstrapping.
%  \begin{itemize}
%	\item For each type of distribution, we randomly selected $n$ data points from the empirical
%	distribution with replacement.
%	\item We repeated the fitting procedure described above for each of 200 bootstrap trials.
%  \end{itemize}

%  We calculated macroscopic diffusion coefficients by simulating trajectories orders of
%  magnitude longer than our molecular simulations.
  \noindent For each solute, we simulated 10000 sFBM trajectories for 1 $\mu$s each. 
  \begin{itemize}
	\item We constructed trajectories by simulating	sequences of dwell times and correlated 
	hop	lengths generated based on parameters randomly chosen from our bootstrapped parameter
	distributions.
	\item We propagated each trajectory until the total time reached 1 $\mu$s, and truncated
	the last data point so that the total time exactly equaled 1 $\mu$s. 
    \item Valid comparisons are only possible between fixed length sFBM simulations. The
    power law dwell time behavior gives rise to the aging phenomenon, embodied by
    a decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
    \item We reported the MSD after 1 $\mu$s with corresponding 95 \% intervals
% Following probably better suited for supporting information, if included at all
%	\item We randomly sample Gaussian hop lengths using the
%	\texttt{numpy.random.normal} method of the \texttt{numpy} python package.
%	\item We randomly sampled dwell times from a discrete power law
%	distribution based on the recommendations of Clauset et
%	al.~\cite{clauset_power-law_2009}: 
%	\begin{equation}
%	x = \lfloor
%	(x_{min} - \tfrac{1}{2})(1 - r)^{-1/(\alpha - 1)} + \tfrac{1}{2} \rfloor
%	\label{eqn:discrete_powerlaw_draws}
%	\end{equation}
%	where $r$ is randomly drawn from a uniform distribution which we simulated
%	with \texttt{numpy.random.uniform}.
%	\item We found that thermal noise does not significantly influence the MSD and
%	therefore did not add any noise to the simulated trajectories. (See supporting info)
  \end{itemize}

%BJC: probably don't need to explain this in great detail
%  \noindent We fixed the length of each simulated trajectory so that we could compare the total
%  MSD between different solutes without the influence of the ageing phenomenon.
%  \begin{itemize}
%	\item Ageing is defined by the tendency of the average MSD to decrease
%	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
%	\item The maximum measured dwell time can be no longer than the total length
%	of a simulated trajectory. 
%	\item As measurement time or trajectory length is increased, longer dwell times
%	are incorporated into the calculation, lowering the average MSD. (See supporting
%	info for demonstration)
%	\item We can achieve consistent total MSDs with low uncertainty for
%	simulated trajectories created with a given set of parameters if we fix the
%	trajectory length (as opposed to total number of steps).  
%  \end{itemize}

@@

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identities and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

@@

  \subsection{Simulated Predictions}\label{section:D_macro}

  We extracted values of $\sigma$, $\alpha$ and $H$ for each solute and then
  simulated 10000 solutes trajectories as described in the Methods. The results
  are presented in Table~\ref{table:simulations}.

  % Add MD calculated MSD to this?
  \begin{table}[h]
  \centering
  \begin{tabular}{ccccc}
  \toprule
  System & $\sigma$ ($nm$) & $\alpha$ & $H$ & Simulated MSD ($nm^2$)\\
  \midrule
  Methanol & 0.46 & 0.85 & 0.40 & 55.06 [49.26, 60.58] \\
  Urea & 0.33 & 0.64 & 0.40 & 15.64 [14.08, 17.32] \\
  Ethylene Glycol & 0.35 & 0.64 & 0.36 & 6.30 [5.69, 6.93] \\
  Acetic Acid & 0.28 & 0.51 & 0.43 & 4.11 [3.66, 4.65] \\
  Mercaptoethanol & 0.32 & 0.58 & 0.37 & 2.54 [2.16, 2.93] \\
  Propylene Glycol & 0.26 & 0.50 & 0.43 & 1.94 [1.70, 2.17] \\
  Ethanol & 0.32 & 0.55 & 0.26 & 1.29 [1.14, 1.43] \\
  Propanol & 0.25 & 0.41 & 0.39 & 1.13 [1.01, 1.27] \\
  Glycerol & 0.22 & 0.46 & 0.37 & 1.09 [0.98, 1.20] \\
  Ethyl Acetate & 0.21 & 0.42 & 0.37 & 0.82 [0.74, 0.91] \\
  Acetone & 0.23 & 0.44 & 0.34 & 0.80 [0.70, 0.88] \\
  Dimethyl Sulfoxide & 0.25 & 0.47 & 0.29 & 0.74 [0.65, 0.82] \\
  Tetrose & 0.22 & 0.43 & 0.20 & 0.68 [0.61, 0.75] \\
  Acetamide & 0.27 & 0.52 & 0.21 & 0.56 [0.51, 0.64] \\
  2,3-Dimercapto-1-propanol & 0.20 & 0.38 & 0.37 & 0.53 [0.47, 0.58] \\
  Butanol & 0.19 & 0.41 & 0.33 & 0.42 [0.36, 0.49] \\
  Propylene Carbonate & 0.19 & 0.38 & 0.29 & 0.30 [0.26, 0.34] \\
  Tetrahydrofuran & 0.25 & 0.40 & 0.24 & 0.29 [0.25, 0.34] \\
  Dimethyl Formamide & 0.20 & 0.39 & 0.27 & 0.27 [0.24, 0.31] \\
  Ribose & 0.21 & 0.43 & 0.23 & 0.27 [0.24, 0.31] \\
  \bottomrule
  \end{tabular}
  \caption{We calculated values $\sigma$, $\alpha$ and $H$ from MD simulation
  trajectories and then computed the average ensemble-averaged MSD of 10000 
  simulated trajectories.}\label{table:simulations}
  \end{table}

  It most cases, it is easy to relate $\sigma$, $\alpha$ and $H$ to the simulated
  simulated MSD values presented in Table~\ref{table:simulations}. 
  \begin{itemize}
  	\item Higher values of $\sigma$ indicate larger average hop lengths.
  	\item Higher values of $\alpha$ mean that there will be less sampling of 
  	long dwell times.
  	\item Values of $H$ near the Brownian limit of 0.5, indicate a lower degree
  	of anti-correlation.
  	\item All of which contribute to an overall increase in the simulated MSD
  \end{itemize}

@@

  \clearpage

  \bibliographystyle{ieeetr}
  \bibliography{transport}
